%Threats to validity
% scenario more dynamic
% other variables change

Basically, the methodology applied in this study was action research to explore weaknesses and not answered questions related to C2 Agility and its challenges. The SPL approach applied to prospect the solution proposed required some simplification in the original problem and context. Thus, for this process, the following threats to validity and corresponding mitigation strategies are presented in the following: 

\begin{itemize}
   \item \textbf{Conclusion validity}: The C2 Context is a complex scenario with plenty of variables and constraints with high level of interdependence and uncertainty. To simplify this context aiming to get a mathematical model, we defined some assumptions to reduce the problem scope. To minimize the loosing of some important factor that impact in results, we checked with domain specialists some possible real scenarios isolating variables and constraints to identify their importance and weight in execution.
   
   \item \textbf{Internal validity}: Considering the complexity involved with C2 Context, the mathematical models and simulation tools are not able to treat all variables and constraints existing in real scenario. Simpler models can hide important effects of some variables and be incompatible with real scenarios. To mitigate this risk, we are composing more than one model to represent the dynamic and static view, in addition to represent roles,interaction and dependences . Furthermore, we are planning to use more than one simulation tool in order to compare results and behaviour to get closer to real scenario conditions.
   
   \item \textbf{Construct validity}: To assure that the network structures chosen were suitable to simplify NEC approach applied to the five maturity levels in C2 Approach Space, all connectivity characteristics of each C2 approach were analyzed and compared with each network topology used as approximation. Additionally, mixed structures with complex nodes connections were ignored to becomes the solution feasible.
   
   
   \item \textbf{External validity}: C2 context is a broad knowledge area and it can be applied in many different circumstances and scenarios, e.g., Civil Defense, Military operations, financial control and natural disasters plan treatment. This large number of possibilities reserves specific characteristics of each scenario that can become unfeasible a \textit{``one size fits all''} solution. Based on this limitation, the scope of this work was limited to C2 applied to military context.
\end{itemize}